Plots for Latent Hawkes Paper

### 2020-07-09 output_scripts/Paper_Plots.Rmd
update diagnostics and paper plots
update the paper plots

---
title: "Plots for Latent Hawkes Paper"
author: "Owen G. Ward"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/", echo = FALSE, include = FALSE,
                     message=FALSE)
# setting these to false to only show updates
knitr::opts_chunk$set(message = FALSE)
```

```{r, load_packages, include=FALSE}

# don't write to this path
orig_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part2/real_data/"

new_data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_orig_code/"

func_dir <- "C:/Users/owenw/Dropbox/with Owen/code/part2/lib/"

@@

```{r more_setup}
#data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_copy/"
jing_data_path <- "C:/Users/owenw/Google Drive/Tian/Research+JingWu/thesis_data/part2/real_data/"
plot_path = "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/plots/"

```{r,echo=FALSE,include=FALSE}
full_data <- readRDS("C:/Users/owenw/Dropbox/with Owen/code/part2/data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

@@

The aim of this notebook is a way to quickly and efficiently create all the plots
required for this paper. We will currently build them using the refit version of Jing's fit,
which ignored windows with no events (to confirm we can recreate that exactly).

```{r}
data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/debug_copy/"
```

@@

```{r}
current_cohort <- 1
png(paste(plot_path,"contour.png",sep=""),width=480,height=480)
load(paste(jing_data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)
z.func <- function(x,y){
  return(x*y*eta1_mean*exp(-eta2_mean*abs(x-y))/(1+exp(-eta3_mean*(y-x))))
  # this is because axes are flipped that we have y-x in last term
  #return(x*y*eta1_mean/(1+exp(eta2_mean*abs(x-y)-eta3_mean*(y-x))))
}
z_plot <- outer(seq(1,0,-0.01),  
                seq(0,1,0.01), 
                z.func)
my.image.plot(seq(0,1,0.01), seq(0,1,0.01), z_plot,
              xlab=expression(f[j]),ylab=expression(f[i]),
              my.main="(a)", cex.main=2.3, 
              cex.lab=2.5, xLabels=c(1,0), yLabels=c(0,1))
dev.off()

my.image.plot(seq(0,1,0.01), seq(0,1,0.01), z_plot,
              xlab=expression(f[j]),ylab=expression(f[i]),
              my.main="(a)", cex.main=2.3, 
              cex.lab=2.5, xLabels=c(1,0), yLabels=c(0,1))

@@

```{r,echo=FALSE}
load(paste(jing_data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)
f_est <- apply(sim_cohort_hp$f,2,mean)
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
                   observe=list(observe.id),
                   observe.length=list(observe.time),
                   no.events=list(no.events))
unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])

@@

png(paste(plot_path,"/diagonsis_model1_",cohort_names[current_cohort],".png",sep=''),
    width=480,height=480)
# -------------- KS plot (stat)
col.vec <- cRamp(as.vector(ks.stat.matrix))
## need to do some sort of transformation between these here
vir_cols <- viridis::viridis(length((as.vector(ks.stat.matrix))))
#order(as.vector(ks.stat.matrix),method = "")

@@

mtext(text=expert_rank_10[[current_cohort]], side=1, line=1.8, outer=TRUE, cex=1.8,
      at=1/14*c(1:12)-1/22)
mtext(text=expert_rank_10[[current_cohort]], side=2, line=0.5, outer=TRUE, cex=1.8,
      at=1/12*c(12:1)-1/20, las=2)
mtext(text="(b)", side=3, line=1.4, outer=TRUE, cex=2.2,
      at=0.45, font=2)
dev.off()
```

@@

```{r}
load(paste(jing_data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
gamma_mean <- apply(sim_cohort_dchp$gamma,2,mean)
zeta_mean <- apply(sim_cohort_dchp$zeta,2,mean)

@@

png(paste(plot_path,"/lambda0_",cohort_names[current_cohort],".png",sep=''),
    width=400, height=300)
matrixPlotParameter(latent_social_matrix[rev(expert_rank_10[[current_cohort]]),expert_rank_10[[current_cohort]]],
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),title="(a)")
mtext(text=c(1,2,11,6,7,9), side=1, line=-0.35, outer=TRUE, cex=1.3,
      at=1/17.8*seq(2,12,2)+0.09)
dev.off()
```
## Figure 3b: Ranking Comparison

```{r}
current_cohort <- 1
colors_plot <- viridis(2)
load(paste(jing_data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(jing_data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
png(paste(plot_path,"/rank_",cohort_names[current_cohort],".png",sep=''),
    width=400, height=300)
par(oma = c(0,0,2,0), mar = c(3,4,1,1),mgp=c(0,0.5,0))
plot(order(expert_rank_10[[current_cohort]]),
     apply(sim_cohort_hp$f,2,mean),pch=16,cex=1.2,
     #col= "steelblue", 
     col = colors_plot[1],
     ylab="",xlab="",
     xlim=c(1,12.5),ylim=c(0,1), xaxt="n", yaxt="n")
segments(order(expert_rank_10[[current_cohort]]),
         apply(sim_cohort_hp$f,2,mean)-apply(sim_cohort_hp$f,2,sd),
         order(expert_rank_10[[current_cohort]]),
         apply(sim_cohort_hp$f,2,mean)+apply(sim_cohort_hp$f,2,sd),
         #col= add.alpha("steelblue",0.8),lwd=2)
         col = add.alpha(colors_plot[1],0.8), lwd =2)
points(order(expert_rank_10[[current_cohort]])+0.2,
       apply(sim_cohort_dchp$f,2,mean),
       pch=16,cex=1.2,
       col=colors_plot[2])
       #col="goldenrod2")
segments(order(expert_rank_10[[current_cohort]])+0.2,
         apply(sim_cohort_dchp$f,2,mean)-apply(sim_cohort_dchp$f,2,sd),
         order(expert_rank_10[[current_cohort]])+0.2,
         apply(sim_cohort_dchp$f,2,mean)+apply(sim_cohort_dchp$f,2,sd),
         col= add.alpha(colors_plot[2],0.8),lwd=2)
         #col= add.alpha("goldenrod2",0.8),lwd=2)

@@

axis(LEFT <-2, at=seq(0,1,0.2), labels=seq(0,1,0.2), las= HORIZONTAL<-1,
     cex.axis=1.3, tck=-0.015)
mtext(side=1, text="I&SI rank", line=1.8, cex=1.5)
mtext(side=2, text="Latent rank", line=2.4, cex=1.6)
mtext(side=3, text="(b)", line=0.8, cex=1.6, font=2)
legend('bottomleft', legend = c("C-HP", "C-DCHP"), 
       pch = c(16, 16), lty = c(1, 1), lwd=c(2,2),
       #col=c("steelblue","goldenrod"),
       col=c(colors_plot[1],colors_plot[2]),
       cex=1.5)
dev.off()
```
# Figure 4:
To be added.

@@

```{r}
### Rank Comparison for Single Cohort ####
current_cohort <- 1

load(paste(jing_data_path,cohort_names[current_cohort],
           "/agg_rank_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(jing_data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(jing_data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(jing_data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

@@

png(paste(plot_path,"real_rank_one_cohort.png",sep=""),width=600,height=300)

p1 <- ggplot(plot_latent_df, aes(x = Mice, y = force, fill = Method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(4))+
  #scale_fill_manual(values = c("gray", "steelblue", "goldenrod2" , "firebrick2")) + 
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 11),
        legend.position="none") +
  facet_grid(cols=vars(Method)) +
  xlab("Mice (ranked by I&SI method)") + 
  ylab("Latent rank")
p1
dev.off()
p1
beepr::beep()
```
## Figure 6b: Spearman rank correlation

@@

# Figure 7: Pearson residual matrices

Here is where I need to be a bit more careful about using the correct fits.
Currently using all from Jing's saved output.

In the process of updating this to compute the PR for C-mmhp and I-mmhp on the cluster and simply load those matrices.

```{r}
current_cohort <- 1

m1_residual_matrix_lst <- list()
m2_residual_matrix_lst <- list()
m3_residual_matrix_lst <- list()
mmhp_residual_matrix_lst <- list()

  print(current_cohort)
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  return_df <- cleanObservationPeriod(current_cohort, clean_data)
  unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
    summarize(count=n(),
              observe=list(observe.id),
              observe.length=list(observe.time),
              no.events=list(no.events))
  unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])

  # M1
  load(paste(jing_data_path,cohort_names[current_cohort],
             "/cohort_hp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))
  model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0),
                         eta_1=mean(sim_cohort_hp$eta_1),
                         eta_2=mean(sim_cohort_hp$eta_2),
                         eta_3=mean(sim_cohort_hp$eta_3),
                         beta=mean(sim_cohort_hp$beta),
                         f=apply(sim_cohort_hp$f,2,mean))
  model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0,
                                                  nrow=mice_number,ncol=mice_number),
                            alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
                                                                                      model1_par_est$eta_1,
                                                                                      model1_par_est$eta_2,
                                                                                      model1_par_est$eta_3),
                                                    model1_par_est$f),
                            beta_matrix=matrix(model1_par_est$beta,
                                               nrow=mice_number,ncol=mice_number))
  m1_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)

  for(i in 1:mice_number){
    for(j in 1:mice_number){
      pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
      if(length(pair)>0&(i!=j)){
        par_est <- lapply(model1_par_matrix, function(x) x[i,j])
        names(par_est) <- c("lambda0","alpha","beta")
        current_window_vec <- unique_pairs_df$observe[[pair]]
        all_residual <- 0
        for(cur in c(1:length(current_window_vec))){ ## check length > 2
          cur_win <- current_window_vec[cur]
          current_event_time <- return_df[return_df$initiator==i&
                                            return_df$recipient==j&
                                            return_df$observe.id==cur_win,"event.times"][[1]]
          current_obs_time <- return_df[return_df$initiator==i&
                                          return_df$recipient==j&
                                          return_df$observe.id==cur_win,"observe.time"]
          all_residual <- all_residual + uniHawkesPearsonResidual(object=par_est,
                                                                  events=current_event_time,
                                                                  termination = current_obs_time)
        }
        m1_residual_matrix[i,j] <- all_residual
      }
    }
  }

  # M2
  load(paste(jing_data_path,cohort_names[current_cohort],
             "/cohort_dchp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))
  model2_par_est <- list(gamma=apply(sim_cohort_dchp$gamma,2,mean),
                         zeta=apply(sim_cohort_dchp$zeta,2,mean),
                         eta_1=mean(sim_cohort_dchp$eta_1),
                         eta_2=mean(sim_cohort_dchp$eta_2),
                         eta_3=mean(sim_cohort_dchp$eta_3),
                         beta=mean(sim_cohort_dchp$beta),
                         f=apply(sim_cohort_dchp$f,2,mean))
  model2_par_matrix <- list(lambda0_matrix=model2_par_est$gamma%*%t(rep(1,mice_number))+
                              rep(1,mice_number)%*%t(model2_par_est$zeta),
                            alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y,
                                                                                      model2_par_est$eta_1,
                                                                                      model2_par_est$eta_2,
                                                                                      model2_par_est$eta_3),
                                                    model2_par_est$f),
                            beta_matrix=matrix(model2_par_est$beta,
                                               nrow=mice_number,ncol=mice_number))
  m2_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)

  for(i in 1:mice_number){
    for(j in 1:mice_number){
      pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
      if(length(pair)>0&(i!=j)){
        par_est <- lapply(model2_par_matrix, function(x) x[i,j])
        names(par_est) <- c("lambda0","alpha","beta")
        current_window_vec <- unique_pairs_df$observe[[pair]]
        all_residual <- 0
        for(cur in c(1:length(current_window_vec))){ 
          cur_win <- current_window_vec[cur]
          current_event_time <- return_df[return_df$initiator==i&
                                            return_df$recipient==j&
                                            return_df$observe.id==cur_win,"event.times"][[1]]
          current_obs_time <- return_df[return_df$initiator==i&
                                          return_df$recipient==j&
                                          return_df$observe.id==cur_win,"observe.time"]
          all_residual <- all_residual + uniHawkesPearsonResidual(object=par_est,
                                                                  events=current_event_time,
                                                                  termination = current_obs_time)
        }
        m2_residual_matrix[i,j] <- all_residual
      }
    }
  }

This is too large to load at the moment again. Can do this on the cluster.

```{r, eval=FALSE}  
  # M3
  load(paste(jing_data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))
  load(paste(jing_data_path,cohort_names[current_cohort],
             "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep=''))
  model3_par_est <- list(lambda0=mean(sim_cohort_mmhp$lambda0),
                         lambda1=mean(sim_cohort_mmhp$lambda1),
                         eta_1=mean(sim_cohort_mmhp$eta_1),
                         eta_2=mean(sim_cohort_mmhp$eta_2),
                         eta_3=mean(sim_cohort_mmhp$eta_3),
                         beta=mean(sim_cohort_mmhp$beta),
                         f=apply(sim_cohort_mmhp$f,2,mean))
  model3_par_matrix <- list(lambda0_matrix=matrix(model3_par_est$lambda0,
                                                  nrow=mice_number,ncol=mice_number),
                            lambda1_matrix=matrix(model3_par_est$lambda1,
                                                  nrow=mice_number,ncol=mice_number),
                            alpha_matrix=formMatrix(function(x,y) model3_fn$alpha.fun(x,y,
                                                                                      model3_par_est$eta_1,
                                                                                      model3_par_est$eta_2),
                                                    model3_par_est$f),
                            beta_matrix=matrix(model3_par_est$beta,
                                               nrow=mice_number,ncol=mice_number),
                            q1_matrix=formMatrix(function(x,y) model3_fn$q1.fun(x,y,model3_par_est$eta_3),
                                                 model3_par_est$f),
                            q2_matrix=formMatrix(function(x,y) model3_fn$q0.fun(x,y,model3_par_est$eta_3),
                                                 model3_par_est$f))
  m3_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
  no_segments <- 5000 # changed from 5000
  window_pr <- c()
  for(i in 1:mice_number){
    print(i)
    for(j in 1:mice_number){
      pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
      if(length(pair)>0&(i!=j)){
        par_est <- lapply(model3_par_matrix, function(x) x[i,j])
        names(par_est) <- c("lambda0","lambda1","alpha","beta","q1","q2")
        current_window_vec <- unique_pairs_df$observe[[pair]]
        all_residual <- 0

>>>>

---
title: "Plots for Latent Hawkes Paper"
author: "Owen G. Ward"
date: '`r Sys.Date()`'
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: FALSE
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "paper_figure/",
                      dev = 'png', fig.height = 4.5, fig.width = 7,
                      warning = FALSE)
```

```{r load_packages, include=FALSE}

# don't write to this path
data_path <- "../output/"

func_dir <- "../lib/"

@@

```{r load rankings,echo=FALSE,include=FALSE,results='hide',cache=TRUE}
full_data <- readRDS("../data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45
cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

@@

The aim of this notebook is a way to quickly and efficiently create all the plots
required for this paper. They will be built with the current fits and models.

@@

```{r fig-2a-contour-plot}
current_cohort <- 1
#png(paste(plot_path,"contour.png",sep=""),width=480,height=480)
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)
z.func <- function(x,y){
  return(x*y*eta1_mean*exp(-eta2_mean*abs(x-y))/(1+exp(-eta3_mean*(y-x))))
  # this is because axes are flipped that we have y-x in last term
  #return(x*y*eta1_mean/(1+exp(eta2_mean*abs(x-y)-eta3_mean*(y-x))))
}
z_plot <- outer(seq(1,0,-0.01),  
                seq(0,1,0.01), 
                z.func)
my.image.plot(seq(0,1,0.01), seq(0,1,0.01), z_plot,
              xlab=expression(f[j]),ylab=expression(f[i]),
              my.main="(a)", cex.main=2.3, 
              cex.lab=2.5, xLabels=c(1,0), yLabels=c(0,1))

@@

```{r fig-2b-diag-plot,echo=FALSE,warning=FALSE}
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)
f_est <- apply(sim_cohort_hp$f,2,mean)
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
                   observe=list(observe.id),
                   observe.length=list(observe.time),
                   no.events=list(no.events))
unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])

@@

# png(paste(plot_path,"/diagonsis_model1_",cohort_names[current_cohort],".png",sep=''),
#     width=480,height=480)
# -------------- KS plot (stat)
col.vec <- cRamp(as.vector(ks.stat.matrix))
## need to do some sort of transformation between these here
vir_cols <- viridis::viridis(length((as.vector(ks.stat.matrix))))
#order(as.vector(ks.stat.matrix),method = "")

@@

mtext(text=expert_rank_10[[current_cohort]], side=1, line=1.8, outer=TRUE, cex=1.8,
      at=1/14*c(1:12)-1/22)
mtext(text=expert_rank_10[[current_cohort]], side=2, line=0.5, outer=TRUE, cex=1.8,
      at=1/12*c(12:1)-1/20, las=2)
mtext(text="(b)", side=3, line=1.4, outer=TRUE, cex=2.2,
      at=0.45, font=2)
#dev.off()
```

@@

```{r fig-3a-baseline-rate}
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
gamma_mean <- apply(sim_cohort_dchp$gamma,2,mean)
zeta_mean <- apply(sim_cohort_dchp$zeta,2,mean)

@@

# png(paste(plot_path,"/lambda0_",cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
matrixPlotParameter(latent_social_matrix[rev(expert_rank_10[[current_cohort]]),expert_rank_10[[current_cohort]]],
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),title="(a)")
# mtext(text=c(1,2,11,6,7,9), side=1, line=-0.35, outer=TRUE, cex=1.3,
#       at=1/17.8*seq(2,12,2)+0.09)
#dev.off()
```
## Figure 3b: Ranking Comparison

```{r fig-3b-rank-comparison}
current_cohort <- 1
colors_plot <- viridis(2)
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
# png(paste(plot_path,"/rank_",cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
par(oma = c(0,0,2,0), mar = c(3,4,1,1),mgp=c(0,0.5,0))
plot(order(expert_rank_10[[current_cohort]]),
     apply(sim_cohort_hp$f,2,mean),pch=16,cex=1.2,
     #col= "steelblue",
     col = colors_plot[1],
     ylab="",xlab="",
     xlim=c(1,12.5),ylim=c(0,1), xaxt="n", yaxt="n")
segments(order(expert_rank_10[[current_cohort]]),
         apply(sim_cohort_hp$f,2,mean)-apply(sim_cohort_hp$f,2,sd),
         order(expert_rank_10[[current_cohort]]),
         apply(sim_cohort_hp$f,2,mean)+apply(sim_cohort_hp$f,2,sd),
         #col= add.alpha("steelblue",0.8),lwd=2)
         col = add.alpha(colors_plot[1],0.8), lwd =2)
points(order(expert_rank_10[[current_cohort]])+0.2,
       apply(sim_cohort_dchp$f,2,mean),
       pch=16,cex=1.2,
       col=colors_plot[2])
       #col="goldenrod2")
segments(order(expert_rank_10[[current_cohort]])+0.2,
         apply(sim_cohort_dchp$f,2,mean)-apply(sim_cohort_dchp$f,2,sd),
         order(expert_rank_10[[current_cohort]])+0.2,
         apply(sim_cohort_dchp$f,2,mean)+apply(sim_cohort_dchp$f,2,sd),
         col= add.alpha(colors_plot[2],0.8),lwd=2)
         #col= add.alpha("goldenrod2",0.8),lwd=2)

@@

axis(LEFT <-2, at=seq(0,1,0.2), labels=seq(0,1,0.2), las= HORIZONTAL<-1,
     cex.axis=1.3, tck=-0.015)
mtext(side=1, text="I&SI rank", line=1.8, cex=1.5)
mtext(side=2, text="Latent rank", line=2.4, cex=1.6)
mtext(side=3, text="(b)", line=0.8, cex=1.6, font=2)
legend('bottomleft', legend = c("C-HP", "C-DCHP"),
       pch = c(16, 16), lty = c(1, 1), lwd=c(2,2),
       #col=c("steelblue","goldenrod"),
       col=c(colors_plot[1],colors_plot[2]),
       cex=1.5)
#dev.off()
```

# Figure 4:
To be added.

@@

```{r fig-6a-rank-vs-isi}
### Rank Comparison for Single Cohort ####
current_cohort <- 1

load(paste(data_path,cohort_names[current_cohort],
           "/agg_rank_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

@@

# png(paste(plot_path,"real_rank_one_cohort.png",sep=""),width=600,height=300)

p1 <- ggplot(plot_latent_df, 
             aes(x = Mice, y = force, fill = Method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(4))+
  #scale_fill_manual(values = c("gray", "steelblue", "goldenrod2" , "firebrick2")) +
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 10),
        legend.position="none") +
  facet_grid(cols=vars(Method)) +
  xlab("Mice (ranked by I&SI method)") +
  ylab("Latent rank")
p1
#dev.off()

```
## Figure 6b: Spearman rank correlation

@@

<!-- # Figure 7: Pearson residual matrices -->

<!-- Here is where I need to be a bit more careful about using the correct fits. -->
<!-- Currently using all from Jing's saved output. -->

<!-- In the process of updating this to compute the PR for C-mmhp and I-mmhp on the cluster and simply load those matrices. -->

<!-- ```{r} -->
<!-- current_cohort <- 1 -->

<!-- m1_residual_matrix_lst <- list() -->
<!-- m2_residual_matrix_lst <- list() -->
<!-- m3_residual_matrix_lst <- list() -->
<!-- mmhp_residual_matrix_lst <- list() -->

<!--   print(current_cohort) -->
<!--   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
<!--   return_df <- cleanObservationPeriod(current_cohort, clean_data) -->
<!--   unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>% -->
<!--     summarize(count=n(), -->
<!--               observe=list(observe.id), -->
<!--               observe.length=list(observe.time), -->
<!--               no.events=list(no.events)) -->
<!--   unique_observe_win <- unique(return_df[,c("observe.id","observe.time")]) -->

<!--   # M1 -->
<!--   load(paste(jing_data_path,cohort_names[current_cohort], -->
<!--              "/cohort_hp_stan_result_",cohort_names[current_cohort], -->
<!--              ".RData",sep='')) -->
<!--   model1_par_est <- list(lambda0=mean(sim_cohort_hp$lambda0), -->
<!--                          eta_1=mean(sim_cohort_hp$eta_1), -->
<!--                          eta_2=mean(sim_cohort_hp$eta_2), -->
<!--                          eta_3=mean(sim_cohort_hp$eta_3), -->
<!--                          beta=mean(sim_cohort_hp$beta), -->
<!--                          f=apply(sim_cohort_hp$f,2,mean)) -->
<!--   model1_par_matrix <- list(lambda0_matrix=matrix(model1_par_est$lambda0, -->
<!--                                                   nrow=mice_number,ncol=mice_number), -->
<!--                             alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y, -->
<!--                                                                                       model1_par_est$eta_1, -->
<!--                                                                                       model1_par_est$eta_2, -->
<!--                                                                                       model1_par_est$eta_3), -->
<!--                                                     model1_par_est$f), -->
<!--                             beta_matrix=matrix(model1_par_est$beta, -->
<!--                                                nrow=mice_number,ncol=mice_number)) -->
<!--   m1_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->

<!--   for(i in 1:mice_number){ -->
<!--     for(j in 1:mice_number){ -->
<!--       pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
<!--       if(length(pair)>0&(i!=j)){ -->
<!--         par_est <- lapply(model1_par_matrix, function(x) x[i,j]) -->
<!--         names(par_est) <- c("lambda0","alpha","beta") -->
<!--         current_window_vec <- unique_pairs_df$observe[[pair]] -->
<!--         all_residual <- 0 -->
<!--         for(cur in c(1:length(current_window_vec))){ ## check length > 2 -->
<!--           cur_win <- current_window_vec[cur] -->
<!--           current_event_time <- return_df[return_df$initiator==i& -->
<!--                                             return_df$recipient==j& -->
<!--                                             return_df$observe.id==cur_win,"event.times"][[1]] -->
<!--           current_obs_time <- return_df[return_df$initiator==i& -->
<!--                                           return_df$recipient==j& -->
<!--                                           return_df$observe.id==cur_win,"observe.time"] -->
<!--           all_residual <- all_residual + uniHawkesPearsonResidual(object=par_est, -->
<!--                                                                   events=current_event_time, -->
<!--                                                                   termination = current_obs_time) -->
<!--         } -->
<!--         m1_residual_matrix[i,j] <- all_residual -->
<!--       } -->
<!--     } -->
<!--   } -->

<!--   # M2 -->
<!--   load(paste(jing_data_path,cohort_names[current_cohort], -->
<!--              "/cohort_dchp_stan_result_",cohort_names[current_cohort], -->
<!--              ".RData",sep='')) -->
<!--   model2_par_est <- list(gamma=apply(sim_cohort_dchp$gamma,2,mean), -->
<!--                          zeta=apply(sim_cohort_dchp$zeta,2,mean), -->
<!--                          eta_1=mean(sim_cohort_dchp$eta_1), -->
<!--                          eta_2=mean(sim_cohort_dchp$eta_2), -->
<!--                          eta_3=mean(sim_cohort_dchp$eta_3), -->
<!--                          beta=mean(sim_cohort_dchp$beta), -->
<!--                          f=apply(sim_cohort_dchp$f,2,mean)) -->
<!--   model2_par_matrix <- list(lambda0_matrix=model2_par_est$gamma%*%t(rep(1,mice_number))+ -->
<!--                               rep(1,mice_number)%*%t(model2_par_est$zeta), -->
<!--                             alpha_matrix=formMatrix(function(x,y) model1_fn$alpha.fun(x,y, -->
<!--                                                                                       model2_par_est$eta_1, -->
<!--                                                                                       model2_par_est$eta_2, -->
<!--                                                                                       model2_par_est$eta_3), -->
<!--                                                     model2_par_est$f), -->
<!--                             beta_matrix=matrix(model2_par_est$beta, -->
<!--                                                nrow=mice_number,ncol=mice_number)) -->
<!--   m2_residual_matrix <- matrix(0,ncol=mice_number,nrow=mice_number) -->

<!--   for(i in 1:mice_number){ -->
<!--     for(j in 1:mice_number){ -->
<!--       pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j) -->
<!--       if(length(pair)>0&(i!=j)){ -->
<!--         par_est <- lapply(model2_par_matrix, function(x) x[i,j]) -->
<!--         names(par_est) <- c("lambda0","alpha","beta") -->
<!--         current_window_vec <- unique_pairs_df$observe[[pair]] -->
<!--         all_residual <- 0 -->
<!--         for(cur in c(1:length(current_window_vec))){  -->
<!--           cur_win <- current_window_vec[cur] -->
<!--           current_event_time <- return_df[return_df$initiator==i& -->
<!--                                             return_df$recipient==j& -->
<!--                                             return_df$observe.id==cur_win,"event.times"][[1]] -->
<!--           current_obs_time <- return_df[return_df$initiator==i& -->
<!--                                           return_df$recipient==j& -->
<!--                                           return_df$observe.id==cur_win,"observe.time"] -->
<!--           all_residual <- all_residual + uniHawkesPearsonResidual(object=par_est, -->
<!--                                                                   events=current_event_time, -->
<!--                                                                   termination = current_obs_time) -->
<!--         } -->
<!--         m2_residual_matrix[i,j] <- all_residual -->
<!--       } -->
<!--     } -->
<!--   } -->

<!-- ```   -->

<!-- This is too large to load at the moment again. Can do this on the cluster. -->

<!-- ```{r, eval=FALSE}   -->
<!--   # M3 -->
<!--   load(paste(jing_data_path,cohort_names[current_cohort], -->
<!--              "/cohort_mmhp_stan_result_",cohort_names[current_cohort], -->
<!--              ".RData",sep='')) -->
<!--   load(paste(jing_data_path,cohort_names[current_cohort], -->
<!--              "/cmmhp_est_zt_",cohort_names[current_cohort],".RData",sep='')) -->
<!--   model3_par_est <- list(lambda0=mean(sim_cohort_mmhp$lambda0), -->
<!--                          lambda1=mean(sim_cohort_mmhp$lambda1), -->
<!--                          eta_1=mean(sim_cohort_mmhp$eta_1), -->
<!--                          eta_2=mean(sim_cohort_mmhp$eta_2), -->
<!--                          eta_3=mean(sim_cohort_mmhp$eta_3), -->
<!--                          beta=mean(sim_cohort_mmhp$beta), -->
